---
title: "Doer Reports in R"
output:
  html_document
---

## Dependency and Notes

    > `install.packages("tidyverse")`
    > `install.packages("dplyr")`
    > `install.packages("ggplot2")`
    > `install.packages("grid")`
    > `install.packages("plotly")`
    > `install.packages("RPostgreSQL")`
    > `install.packages("sqldf")`
    > `install.packages("ggthemes")`
    > `install.packages("ggrepel")`
    > `install.packages("gridExtra")`
    > `install.packages("glue")`
    > `install.packages("stringr")`
    > `install.packages("stringi")`
    > `install.packages("scales")`
    > `install.packages("flextable")`
    > `install.packages("officer")`

Load the **tidyverse** library for dplyr, ggplot2 and other things
Load the **dplyr** library for dplyr
Load the **ggplot2** library for ggplot2
Load the **ggplot2** library for plot grid manipulation
Load the **plotly** library for plotly
Load the **RPostgreSQL** library for accessing database
Load the **sqldf** library for sql support in data frames
Load the **ggthemes** library for graph themes
Load the **ggrepel** library for text placement in graphs
Load the **gridExtra** library for layouting graphs
Load the **glue** library for string formatting
Load the **stringr** library for string operations
Load the **stringi** library for string operations
Load the **scales** library for axis label scaling
Load the **flextable** library for axis label scaling
Load the **officer** library for formatting tables/cells

```{r warning=FALSE}
#library(tidyverse)
library(dplyr)
library(ggplot2)
library(grid)
library(plotly)
library(RPostgreSQL)
library(sqldf)
library(ggthemes)
library(ggrepel)
library(gridExtra)
library(glue)
library(stringr)
library(stringi)
library(scales)
library(flextable)
library(officer)
```

define the parameters for the report
```{r}
fromdate <- "Jun-01-2017"
todate <- "Dec-31-2017"
agentname_pattern <- "%"
branchname_pattern <- "S%"
```

define the query for the reportß
```{r}
sql <- glue("select r.branchOid, r.agentOid, b.branchName, a.agentName, r.servicePointOid, count(*), sum(r.actualAmountInBdt)
from 	Remittance r join Agent a on r.agentOid = a.oid join Branch b on r.branchOid = b.oid
where r.applicationDate between '{fromdate}' and '{todate}' and a.agentName like '{agentname_pattern}' and b.branchName like '{branchname_pattern}'
group by r.branchOid, r.agentOid, b.branchName, a.agentName, r.servicePointOid;")
```

set the connection password and other settings
```{r}
dbname <- "agrani"
host <- "192.168.0.74"
port <- 5432
user <- "absprod"
pw <- {"absprod"}
```

load the PostgreSQL driver
```{r}
drv <- dbDriver("PostgreSQL")
```

create a connection to the postgres database
```{r}
con <- dbConnect(drv, dbname = dbname, host = host, port = port, user = user, password = pw)
```

removes the password
```{r}
rm(pw)
```

check for the existence of Remittance table (postgres makes names lowercase)
```{r}
dbExistsTable(con, "remittance")
```

get the data into a data frame
```{r}
remittance <- dbGetQuery(con, sql)
```

make a ggplot
```{r}
g1 <- remittance %>% ggplot(aes(x = agentname, y = sum))
```

make a bar/column chart where y axis is agent and x axis is amount
```{r}
p <- g1 + 
  geom_col() +
  ylab("Amount in BDT") +
  xlab("Agent") +
  scale_y_continuous(labels = comma) +
  scale_x_discrete(labels = wrap_format(15)) +
  geom_label(aes(label=comma(sum, nsmall=2)), size=2, position=position_dodge(width=0.9), vjust=0.50) +
  ggtitle(glue("Remittance by Agent between {fromdate} and {todate}")) +
  facet_grid(branchname ~ ., scales = "free_y", space = "free_y", switch = "y", shrink=TRUE, labeller = label_wrap_gen(width=15)) +
  coord_fixed(ratio = 0.1) + 
  coord_flip(expand = FALSE) + 
  theme(strip.text.y = element_text(size = 8, angle = 180, hjust = 0), axis.text.y = element_text(size = 8))

#(gg <- ggplotly(p))
p
```

make a bar/column chart where x axis is agent and y axis is amount
```{r}
p <- g1 + 
  geom_col() +
  #geom_text_repel() +
  ylab("Amount in BDT") +
  xlab("Agent") +
  scale_y_continuous(labels = comma) +
  scale_x_discrete(labels = wrap_format(15)) +
  geom_label(aes(label=comma(sum, nsmall=2)), size=2, position=position_dodge(width=0.9), vjust=0.50) +
  ggtitle(glue("Remittance by Agent between {fromdate} and {todate}")) +
  #facet_wrap(~branchname, scales = "free_x", shrink=TRUE) +
  facet_grid(~branchname, scales = "free_x", space = "free_x", shrink=TRUE) +
  theme(strip.text.x = element_text(size = 8, angle = 90, vjust = 0.50), axis.text.y = element_text(size = 8), axis.text.x = element_text(size = 8, angle = 45, vjust = 0.50))

#(gg <- ggplotly(p))
p
```

Get the ggplot grob
```{r eval=FALSE, include=FALSE}
gp <- ggplotGrob(p)
#grid.ls(grid.force(gp))

# Edit the grob
gp <- editGrob(grid.force(gp), gPath("GRID.stripGrob", "GRID.text"), grep = TRUE, global = TRUE, just = "right", x = unit(0, "npc"))

# Draw it
grid.newpage()
grid.draw(gp)
```

make a tabular view of the data
```{r}
h <- data.frame(
  col_keys = c("branchname", "agentname", "count", "sum"),
  h1 = c("Branch", "Agent", "Disbursement", "Disbursement"),
  h2 = c("Branch", "Agent", "#", "BDT"), stringsAsFactors = FALSE)

t <- remittance %>% 
  arrange(branchname) %>% 
  regulartable(col_keys = c("branchname", "agentname", "count", "sum" )) %>% 
  set_header_df(mapping = h, key = "col_keys") %>% 
  merge_h(part = "header") %>% 
  merge_v(j = "branchname", part = "header") %>% 
  merge_v(j = "agentname", part = "header") %>% 
  merge_v(j = c("branchname")) %>% 
  bg(bg = "gray70", part = "header") %>% 
  color(color = "gray30", part = "header") %>% 
  bold(part = "header") %>% 
  fontsize(size = 12, part = "header") %>% 
  color(i = ~ sum <= 0, color="red") %>% 
  padding(padding.left = 4, part = "all") %>% 
  padding(j = "sum", padding.right = 4, part = "all") %>% 
  align(j = "branchname", align = "left", part = "all" ) %>% 
  align(j = "agentname", align = "left", part = "all" ) %>% 
  align(j = "count", align = "center", part = "all" ) %>% 
  align(j = "sum", align = "right", part = "all" ) %>% 
  set_formatter(sum = function(x) comma(x), count = function(x) comma(x, nsmall=0)) %>% 
  border_outer(border = fp_border(color="gray"), part = "all") %>% 
  border_inner_h(border = fp_border(color="lightgray"), part = "all") %>% 
  border_inner_v(border = fp_border(color="lightgray"), part = "header") %>% 
  autofit()

t
#print(t, preview = "html")
```
